A sheaf--function dictionary for algebraic tori over non-archimedean local fields

### 2013-08-16 shanghai.tex
Fixing some bibilography stuff

%\begin{proposition}\label{tensor}
The category $\QC(G)$ of quasicharacter sheaves on $G$ is rigid symmetric monoidal category \cite{etingof:tensorcat} under the tensor product
$\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$
with duals given by applying the functor 
$\sheafHom(\ - \ ,\EE)$ (sheaf hom) to
conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
%\end{proposition}
(The category of characters sheaves on $G$ is not abelian, so $\QC(G)$
is not a tensor category in the sense of \cite{deligne:02a}.)
%\begin{proof}\end{proof}
%
This rigid monoidal category structure for $\QC(G)$ puts a group
structure on the set $\QCiso{G}$ of isomorphism classes in
$\QC(G)$. Our main result regarding quasicharacter sheaves on $G$ (Theorem~\ref{thm:snake})
determines $\QCiso{G}$ under the hypothesis that the component group scheme for $G$ is geometrically finitely generated; see Theorem~\ref{thm:snake}. To do this, we use the trace of Frobenius.

>>>>

%\begin{proposition}\label{tensor}
The category $\QC(G)$ of quasicharacter sheaves on $G$ is rigid symmetric monoidal category \cite{etingof:09a} under the tensor product
$\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$
with duals given by applying the functor 
$\sheafHom(\ - \ ,\EE)$ (sheaf hom) to
conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
%\end{proposition}
(The category of characters sheaves on $G$ is not abelian, so $\QC(G)$
is not a tensor category in the sense of \cite{deligne:02a}.)
%\begin{proof}\end{proof}
%
This rigid monoidal category structure for $\QC(G)$ puts a group
structure on the set $\QCiso{G}$ of isomorphism classes in
$\QC(G)$. Our main result regarding quasicharacter sheaves on $G$ (Theorem~\ref{thm:snake})
determines $\QCiso{G}$ under the hypothesis that the component group scheme for $G$ is geometrically finitely generated; see Theorem~\ref{thm:snake}. To do this, we use the trace of Frobenius.
